---
title: "height22heights"
author: "Jonathan Lucas"
date: "2023-02-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
theme_set(theme_bw())
```


```{r}
height <- read.csv("CFRF22heights.csv")
height <- height%>%filter(site!="Wilmington")
height$site <- as.factor(height$site)
height$ploidy <- as.factor(height$ploidy)
height$line <- as.factor(height$line)
height$date <- as.Date(height$date, format = "%m/%d/%Y")
#'height$bag' needs to stay a character vector for now
```

Make bag numbers consistent across the experiment, despite Pasture Point bag switch on June 7. bags 97,90,99,15,47,48 kept their original numbers.
```{r}
height <- height %>% mutate(bag = replace(bag, bag == "128", "65"))
height <- height %>% mutate(bag = replace(bag, bag == "139", "76"))
height <- height %>% mutate(bag = replace(bag, bag == "140", "17"))
height <- height %>% mutate(bag = replace(bag, bag == "125", "85"))
height <- height %>% mutate(bag = replace(bag, bag == "138", "87"))
height <- height %>% mutate(bag = replace(bag, bag == "129", "96"))
```

We split Pasture Point 3N NC on August 3.
```{r}
height <- height %>% mutate(bag = replace(bag, bag == "15 and 81", "15"))
height <- height %>% mutate(bag = replace(bag, bag == "47 and 87", "47"))
height <- height %>% mutate(bag = replace(bag, bag == "48 and 84", "48"))
```

We also split Straits 3N NC on September 27.
```{r}
height <- height %>% mutate(bag = replace(bag, bag == "147 and 43", "147"))
height <- height %>% mutate(bag = replace(bag, bag == "148 and 41", "148"))
height <- height %>% mutate(bag = replace(bag, bag == "149 and 44", "149"))

height$bag <- as.factor(height$bag)
```

Because all we want to do here is calculate summary statistics on shell heights that we have measured, we can drop all 'NA'. (Could also have used 'tidyr::drop_na')
```{r}
height <- height[!is.na(height$height),]
```

Create one column for genotype
```{r}
height <- height %>% unite(genotype, c(line, ploidy), sep = " ", remove = FALSE)
```



Now calculate and plot the means.
```{r}
heightmeans <- height %>% group_by(site,date,genotype) %>% summarise(mean(height))
heightmeans <- heightmeans %>% rename(mean = 'mean(height)')
```

```{r}
ggplot(heightmeans, aes(x=date, y=mean, color = genotype)) +
  geom_line(size=1) +
  facet_wrap(~site) +
  scale_x_date(date_breaks = "month") +
  theme(axis.text.x = element_text(angle = 80, vjust = 1, hjust = 1, size = 6)) +
  labs(y = "Mean Shell Height", x = NULL, color = NULL)
```


